Some forms of uncertainty may suppress the evolution of social learning

### 2022-04-11 ms.tex
added 3x3 spread of main results plots

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[width=\textwidth]{{Figures/SL_over_u_lowpayoff=0.1.pdf}}
  \caption{}
  \label{fig:results_pilow_0p1}
  \end{subfigure}

  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[width=\textwidth]{{Figures/SL_over_u_lowpayoff=0.5.pdf}}
  \caption{}
  \label{fig:}
  \end{subfigure}

  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[width=\textwidth]{{Figures/SL_over_u_lowpayoff=0.8.pdf}}
  \caption{}
  \label{fig:}
  \end{subfigure}

  \caption{Dependence of Social Learning ($\langle s \rangle$) on environmental
  variability $u$ for several values of low payoff $\pi_{low}$ and steps per
  round, $M$. $\langle s \rangle$ decreases monotonically for $\pi_{low} = 0.1, 0.5$,
but noise dominates the results for $\pi_{low}=0.8$. When $\pi_{low} = 0.5$, 
the sigmoid is not as sharp as for $\pi_{low}=0.1$, meaning that social learning
is reduced for smaller $u$ and increased for larger $u$.}
  \label{fig:results}
\end{figure}

>>>>

\include{mainResultsPlots.tex}
